IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-05-09 codes/R/paper/cohorts_nc.Rnw
add raw score histograms
add new graph by mother employment, add histograms

@@

\clearpage
\begin{figure}
\begin{center}
<<INCINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=4, fig.width=4, out.width='.5\\linewidth'>>=
@
\end{center}
\caption{Evolution of income inequality }
{\scriptsize \emph{Notes}:  \par}
\end{figure}
% 
% \begin{figure}
% <<FACINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
% @
% \caption{Mean scores across income quintiles}\label{fig:meanci}
% {\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across the quintiles in the income distribution. \par}
% \end{figure}

\begin{figure}
<<FACINEQ_SC, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Mean scores across social class}\label{fig:meanci_sc}
{\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across the quintiles in the income distribution. \par}
\end{figure}

@@

\clearpage
\section{Summary statistics}
\begin{table}[ht]
\caption{Summary statistics} \label{tab:lvpars}
\centering
<<SUMSTATS, results='asis'>>=
require(dummies)

datacompl <- scores2plot[complete.cases(scores2plot[,decvars2]),] # complete cases
# expand dummies
datasum <- cbind(
  datacompl[,c("EXT","INT","cohortsex")], 
  dummy.data.frame(datacompl[,c(decvars2)], sep = "")
)

>>>>

\clearpage
\begin{figure}
<<RAWHIST, dev='tikz', fig.height=10, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Frequency of Raw Scores}
{\scriptsize \emph{Notes}: The figure shows frequencies of raw (sum) scores separately by cohort. Raw scores are obtained using the same 11 items in the CFA model, building a categorical index. Children for which each behaviour ``certainly applies/true" are assigned zero points, one point for ``somewhat applies/true" and two points for ``does not apply/not true". For binary items, one point is assigned for ``true". The raw scores are the sum of the points across the 11 behaviours considered, six for EXT and five for INT. \par}
\end{figure}

@@

\clearpage
\begin{figure}
\begin{center}
<<INCINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=4, fig.width=4, out.width='.5\\linewidth'>>=
@
\end{center}
\caption{Evolution of income inequality }
{\scriptsize \emph{Notes}:  \par}
\end{figure}

<<FACINEQ_DEMEAN>>=
# function for demeaning
@

% 
% \begin{figure}
% <<FACINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
% @
% \caption{Mean scores across income quintiles}\label{fig:meanci}
% {\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across the quintiles in the income distribution. \par}
% \end{figure}

\begin{figure}
<<FACINEQ_SC, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Mean scores across social class}\label{fig:meanci_sc}
{\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across harmonised social class of the cohort member's family at 10 years of age. \par}
\end{figure}

\begin{figure}
<<FACINEQ_YS, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Mean scores across maternal schooling}\label{fig:meanci_ys}
{\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across grouped years of schooling of the cohort member's mother at 5 years of age. \par}
\end{figure}

\begin{figure}
<<FACINEQ_ME, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Mean scores across maternal employment}\label{fig:meanci_me}
{\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval by employment status of the cohort member's mother at 5 years of age. \par}
\end{figure}

@@

\clearpage
\section{Summary statistics}
\begin{table}[ht]
\caption{Summary statistics} \label{tab:lvpars}
\centering
<<SUMSTATS, results='asis'>>=

datacompl <- scores2plot[complete.cases(scores2plot[,decvars]),] # complete cases
# expand dummies
datasum <- cbind(
  datacompl[,c("EXT","INT","cohortsex")], 
  dummy.data.frame(datacompl[,c(decvars)], sep = "")
)
